% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt, a4paper, sans]{moderncv}      
\moderncvstyle{classic}	% [casual, classic, oldstyle, banking]
\moderncvcolor{green}		% [blue, orange, green red, purple, grey, black]
\usepackage{xcolor}
\definecolor{LinkBlue}{RGB}{50,50,175}
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}	% date column width

\name{Gary}{Paduana}
\address{}{La Jolla, CA}
\phone[mobile]{(501) 712-3141}
\email{gary.paduana@gmail.com}                           
\social[github]{garypaduana}
\homepage{garypaduana.com}
\extrainfo{\href{https://rawgit.com/garypaduana/Resume/master/resume.pdf}{\color{LinkBlue}Latest Version}}

\begin{document}
\makecvtitle

\section{Education}
\cvitem{2007}{Robert Morris University, Moon, PA (Integrated Degree Plan)}{
	\cvlistitem{\textbf{Master of Science}, Information Security and Assurance, \textit{3.96 GPA}}
	\cvlistitem{\textbf{Bachelor of Science}, Software Engineering, \textit{3.81 GPA, Magna Cum Laude}}
}

\section{Skills}
\cvlistitem{Proficient in Java, Groovy, SQL, Python, Bash, Javascript, CSS, and HTML.}
\cvlistitem{Experience with Spring (Boot, Integration, MVC, JPA), Grails, Android, Django, Amazon Web Services, various relational databases and object stores, Bootstrap, and Docker.}
\cvlistitem{Focusing on data-driven, back-end problems that require algorithm design and implementation.}
	
\section{Professional Experience}

\cventry{Present \\ Mar 2017}{Software Engineer, Consultant}{\href{http://yth.org}{{\color{LinkBlue}Youth Tech Health}}}{Oakland, CA}{}{Currently creating a mobile web platform to collect medical screening questionnaires and simplify the process of matching patients with providers who offer specialized care.
	\begin{itemize}	
	\item Using Django, PostgreSQL, Google Maps API, and Bootstrap.
	\item Integrating with existing data stores and external service providers to offer new functionality that will enhance the overall user experience when finding providers, obtaining prescriptions, and following the treatment plan.
	\item Designed with expansion in mind so that Django forms could be generated at run-time from a persisted data model allowing administrators to create new questionnaires without changing code.
	\end{itemize}
}

\cventry{Mar 2017 \\ May 2015}{Software Engineer}{\href{http://www.manifoldtechnology.com}{{\color{LinkBlue}Manifold Technology}}}{Sunnyvale, CA}{}{Helped architect, develop, deploy, and maintain financial services and information security software in a start-up environment.
	\begin{itemize}
		\item Solely responsible for the design and creation of three Android applications to demonstrate the use of our platform.  One focused on account balances and transaction histories with charts and a live view of active trades, another showcased purpose-based access control for sensitive user data, {\href{https://github.com/garypaduana/manifold-api-android-client}{{\color{LinkBlue}and another served as an API client library}}} to help other developers access our public API.
		\item Contributed to the core back-end product, which is an asynchronous and highly concurrent collection of Spring Boot Java applications with RESTful APIs and PostgreSQL and Cassandra data stores.
		\item Managed cloud architecture assets in Amazon Web Services and Microsoft Azure.
		\item Configured and maintained a continuous integration environment with Jenkins that automatically deployed the latest development and QA builds to AWS EC2 instances.
		\item Used Selenium to simulate user activity and interaction with various websites to generate a large volume of data that could be used in machine learning analysis.
		\item Developed web prototypes using Bootstrap, Google Charts, and Pixi 2D graphics to support product demonstrations.
		\item Conducted technical interviews for Deployment Engineers, Software Engineers, and Data Scientists.
	\end{itemize}
}

\cventry{Nov 2014 \\ Jul 2013}{Senior Software Engineer}{Healthesystems}{Tampa, FL}{}{Created new enterprise integration software and enhanced existing customer-facing products and processes.
	\begin{itemize}
		\item Lead development on a new Spring Integration application that reconciled offline, historical billing transactions with the existing claims adjudication system.
		\item Created a process for integrating new vendors into Healthesystems' payment processing system and worked directly with vendor management and development staff.  Assisted multiple vendors in troubleshooting and design as they developed a client application to interface with the exposed SOAP Web Services.
	\end{itemize}
}

\cventry{Apr 2012 \\ Feb 2011}{Senior Software Engineer, Contractor}{General Dynamics \& Aerotek}{Santa Clara, CA}{}{Implemented server-side computational algorithms to support a resource scheduling system.
	\begin{itemize}
		\item Created a utility library used to perform geometric, algebraic, and trigonometric calculations.  One notable component is the computation of the inverse of an $A_{n,n}$ complex matrix using \href{http://en.wikipedia.org/wiki/LU_decomposition}{{\color{LinkBlue}Lower Upper decomposition}} and permutation matrices.
		\item Implemented the \href{http://en.wikipedia.org/wiki/K-means_clustering}{{\color{LinkBlue}K-Means Clustering}} algorithm to optimize resource allocation.
		\item Created a test driver that analyzed currently scheduled system demand and exercised the entire production system with a high volume of events.
		\item Created an application to bulk load $> 10^{10}$ reference values originating in both text and binary encoding into a relational database using connection pooling and multithreading.
	\end{itemize}
}

\cventry{Nov 2010 \\ Sep 2008}{Software Engineer, Contractor}{Northrop Grumman \& Assured Space}{Redondo Beach, CA}{}{Designed, tested, and integrated custom software to fit the needs of an operational satellite environment  (\href{http://en.wikipedia.org/wiki/Space_Tracking_and_Surveillance_System}{{\color{LinkBlue}STSS}}) through pre-launch, launch, and early-orbit test phases.
	\begin{itemize}
		\item Created an application to decode command values from binary receipt files to track changes made to payload memory aboard two satellites as a function of time.
		\item Analyzed communication anomalies and helped to solve a significant operational problem. Created a binary telemetry stream filter to calculate loss rates by looking for malformed data frames.
		\item Wrote a stored procedure to serve time series data to satellite operators with look-behind functionality to identify the last known value just prior to entering the time frame requested for each data series.
		\item Decoded the mission data telemetry stream into subsystem outputs for distribution to specialized analysis teams using an interface control document as reference for bit-level routing.
	\end{itemize}
}

\cventry{Feb 2008 \\ May 2006}{IT Security Analyst, Intern}{Bayer Corporate and Business Services}{Pittsburgh, PA}{}{Provided IT security services including remote access, account management, and reporting; developed software to automate and refine existing manual processes.
	\begin{itemize}
		\item Automated a monthly data maintenance task that compiled usage metrics and user account health information for more than 16,000 employees and hundreds of technology services globally.  This new process and software reduced human involvement time from two days to less than four hours.
		\item Provided ad hoc reporting to global management with custom SQL queries.
	\end{itemize}
}

\section{Personal Projects}

\cventry{Since \\ Jan 2015}{\href{http://www.garypaduana.com}{{\color{LinkBlue}Personal Website}}}{}{}{}{A collection of personal projects and photography samples.  Implemented with Grails and Bootstrap.
	\begin{itemize}
		\item \textit{Capital Gains Calculator} - Analyzes transaction history using FIFO accounting and keeps track of short-term and long-term gains, wash sales, proceeds, and cost basis spanning multiple years of transaction history.
	\end{itemize}
}

\cventry{Nov 2013 \\ Sep 2012}{Android Applications}{}{}{}{Created for fun to explore the Android ecosystem, algorithm design, and full-stack deployment responsibilities.
	\begin{itemize}
		\item {\href{http://garypaduana.com/blockTalk}{{\color{LinkBlue}\textit{Block Talk}}}} - An asocial network that allows users to create text and picture messages on a map that can be viewed by anyone browsing near that location resulting in a hyper-local bulletin board.
		\item \textit{Bit Block } - A business directory for Android that aims to connect local businesses and individuals that accept and trade Bitcoin for goods, services, and local currency.  It is a fork of \textit{Block Talk} with new features.
		\item {\href{http://garypaduana.com/wordSolver}{{\color{LinkBlue}\textit{Word Solver}}}} - A wordsmith assistant that helps solve challenging word games and puzzles.  Served over 20,000 solutions to over 3,000 unique users during its active lifetime.
	\end{itemize}
}

\cventry{Apr 2013 \\ Feb 2013}{Little Rock, Arkansas Crime Reporting Automation}{}{}{}{A crime reporting tool that ingests raw text input from police reports and uses regular expressions and Google Maps API in Groovy and Java SE to parse all relevant information and prepare a clean and concise summary and map view for distribution to an audience of over 20,000 Little Rock, Arkansas residents.}

\cventry{Since \\ Apr 2012}{\href{https://github.com/garypaduana/ProjectEuler}{\color{LinkBlue}Project Euler}}{}{}{}{"A series of challenging mathematical/computer programming problems that will require more than just mathematical insights to solve."
	\begin{itemize}
		\item \href{https://projecteuler.net/profile/gary.paduana.png}{{\color{LinkBlue}Solved 104 problems}} to date to practice algorithm design, problem solving, implementation, and optimization using Java SE, Groovy, and Python.
		\item Focus areas include: sequence analyses, prime factorization, prime generation, very large decimal operations, maximum and minimum distance paths in a graph, calendar and time operations, string analyses (palindromes, reversing, substrings, replacing, searching, pattern detection, permutations, regular expressions, etc.), combinatoric selections, card game simulation and bulk analysis of dealt hands, symbolic simplification of non-trivial fractional expressions, XOR encryption and decryption, Euler's Totient analyses, fraction simplification, ordering within a large collection ($> 10^{11}$ elements), number partitioning, the modeling and statistical analyses of board games, and many other similar subjects.
		\item Currently ranked in the top 1.5\% of members that have been solving problems since 2001.
	\end{itemize}
}

\cventry{Since \\ Jun 2010}{\href{https://github.com/garypaduana/GeneralFileUtility}{{\color{LinkBlue}General File Utility}}}{}{}{}{A Groovy desktop application to improve file management productivity.
	\begin{itemize}
		\item \textit{Duplicate File Finder} - Quickly find duplicate files with a lazily-loaded equals evaluation that fails fast without performing unnecessary IO work whenever possible.
		\item \textit{Bulk Rename} - Rename files with a variety of strategies including Trim, Replace, Date-ify, and Series Editor.  Filter affected files with a regular expression and an individual selection capability.
		\item \textit{Binary Operations} - Analyze binary data in hexadecimal form to compute values for a variety of cryptographic message digests, longitudinal parity of various lengths, alternative representations in other numeric bases, and a variety of character set encodings for textual interpretation.
	\end{itemize}
}

\section{Awards and Honors}{
	\small 
	\cvlistitem{Robert Morris University Presidential Scholarship (5-year academic, full tuition)}
	\cvlistitem{Guaranteed Reserve Forces Duty Scholarship (2-year ROTC, full tuition)}
	\cvlistitem{Dean's List 9 of 10 semesters}
	\cvlistitem{Alpha Chi membership, limited to the top 10 percent of an institution's juniors, seniors, and graduate students.}
}

\section{Military}
	
\cventry{Aug 2011 \\ Dec 2007}{Pennsylvania Army National Guard}{}{}{}{2nd Brigade Headquarters, 28th Infantry Division, Washington, PA
	\begin{itemize}
		\item Brigade S2 assistant, Highest Rank: 1st Lieutenant, O2
		\item Military Intelligence Basic Officer Leadership Course II (Ft. Sill, OK, March 2008 - April 2008)
		\item Military Intelligence Basic Officer Leadership Course III (Ft. Huachuca, AZ, April 2008 - August 2008)
	\end{itemize}
}

\cventry{Dec 2007 \\ Jan 2006}{Reserve Officers' Training Corps, Pennsylvania Army National Guard}{}{}{}{University of Pittsburgh ROTC and simultaneous membership in the Pennsylvania National Guard.
	\begin{itemize}
		\item Cadet commander of the Robert Morris University remote company for 4 semesters leading up to 20 cadet students in daily training operations.
		\item Ranked 4th of 28 cadets commissioning from the University of Pittsburgh in 2007
		\item Distinguished Military Graduate (top 20\% of commissioned officers each year)
		\item Leadership Development and Assessment Course (Ft. Lewis, WA, June 2007 -July 2007)
	\end{itemize}
}

\cventry{Jan 2006 \\ Aug 2003}{US Army Reserves}{}{}{}{660th Transportation Company, Cadiz, OH
	\begin{itemize}
		\item Basic Combat Training (Ft. Benning, GA, May 2004 - July 2004)
		\item Advanced Individual Training (Ft. Bliss, TX, July 2004 - Sept 2004)
	\end{itemize}
}

\iffalse
\section{References}{
	\small 
	\cvdoubleitem{}{Jim Chambers\\Supervisor, Northrop Grumman\\trackgraphic@gmail.com\\706-799-0283}{}{Greg Mumenthaler\\Team Lead, Northrop Grumman\\gmumenth@gmail.com\\310-502-3989}
	\hfill \break 
	\hfill \break
	\cvdoubleitem{}{Robert Gettys\\Coworker, Healthesystems\\bob@bobgettys.com\\757-470-8114}{}{Tyler Pinckard\\Coworker, General Dynamics\\tyler.pinckard@gmail.com\\602-859-0542}
}
\fi

\end{document}